Type-Safe Modular Parsing

### 2016-11-29 paper/paper.tex
Abstract

\newcommand\mixin{\textbf{@Mixin} }
\usepackage{xspace}

@@

Text.

>>>>

\newcommand\mixin{\textbf{@Mixin} }
\newcommand\name{\textbf{Parser}\xspace}
\usepackage{xspace}

@@

  Over the years alot of effort has been put on solving challenging
  extensibility problems, while retaining important software
  engineering properties such as modular type-safety and
  separate compilation. Most previous work focused on
  operations that traverse and process extensible Abtract Syntax Tree
  (AST) structures. However, there is almost no work on operations that
  \emph{build} such extensible ASTs, including \emph{parsing}.

  This paper investigates solutions for the problem of \emph{modular
    parsing}. We focus on \emph{semantic} modularity and not just
  \emph{syntactic} modularity. That is, the solutions should not only
  allow complete parsers to be built out of modular parsing
  components, but also enable the parsing components to be \emph{modularly
  type-checked} and \emph{separately compiled}. We present \name: a parsing
  combinator library that enables modular parsing. The library is
  built on top of a Packrat parsing library, but adds new parsing
  combinators to enable modular parsing. The new parsing combinators 
  employ \emph{delegation-based} techniques and \emph{Object Algebras} 
  to support extensibility. The choice of Packrat parsing over other
  parsing techniques turns out to be important for achieving
  performance in a modular setting. To evaluate \name 
  we conduct a  case study based on the 
  ``Types and Programming Languages'' interpreters. The case study 
  shows that \name is effective at reusing parsing code from existing
  interpreters, and the total parsing code is 60\% smaller than the
  non-modular parsing code.
